\subsection{ISDA Common Domain Model}
\label{subsec:cdm}
The ISDA Common Domain Model (CDM) \citep{isda_cdm_factsheet} is a groundbreaking initiative aimed at bringing uniformity to the financial markets. It addresses the challenges posed by the increasing intricacy of the industry and the pressing need for streamlined operations. The model functions as a comprehensive framework that is both "machine-readable" and "executable." In simpler terms, "machine-readable" means that the data and rules within the CDM can be easily understood by computers without human intervention. "Executable" means that the model can automatically carry out transactions and processes, further reducing manual effort. Being an open-source project, the CDM is freely accessible and can be modified to suit the specific needs of different organizations in the financial sector. This adaptability is particularly beneficial for industry participants looking for tailored solutions. 

One of the primary objectives of the CDM is to enhance operational efficiency in financial markets. It does this by setting a digital standard for various trading activities and events. This uniform standard makes it easier for different companies and platforms to interact with each other, thereby minimizing the discrepancies that often require time-consuming reconciliation.

Transparency is another cornerstone of the CDM. It ensures that regulatory bodies and market participants are aligned, which is crucial for consistent reporting to authorities. The model is built on foundational design principles such as "abstraction-based normalization," which means simplifying complex elements to their most basic forms; "composability," or the ability to combine different components seamlessly; and "modularization," which allows for easy updates and modifications. These principles contribute to the robustness and flexibility of the CDM.

Governed by a structured set of guidelines, the CDM is applicable to a broad spectrum of financial products, including but not limited to Over-The-Counter (OTC) derivatives and cash securities. The model comprises various elements, including the publicly accessible ISDA CDM Distribution \citep{cdm_distribution_github}, the specialized Rosetta Domain-Specific Language (DSL) \citep{rosetta_dsl}, and a supportive ecosystem of applications built on the CDM framework \citep{applications_cdm}.